Comparing software variability across and within fMRI analysis packages

### 2022-01-25 paper/paper.tex
Fix ref

\begin{equation}
  N = (-1)^s \times 2^E \times (1.m),
\end{equation}
where $E=e-127$ for single precision and $E=e-1023$ for double precision.
In single precision, the pseudo-mantissa has 23 bits and the exponent has 8 bits, whereas in 
double precision the pseudo-mantissa has 52 bits and the exponent has 11 bits. 
Machine error, the smallest absolute difference between two
floating-point numbers that can be represented, is in general $2^{-24}\times e$ in
single precision and $2^{-53}\times e$ in double precision.
We simulated machine error by introducing the random perturbation defined
in Equation~\ref{eq} at the virtual precision of $t=24$~bits for single-precision 
values and $t=53$~bits for double-precision ones. The perturbed pseudo-mantissa
is obtained by extending the size of the original pseudo-mantissa, applying the perturbation 
at the desired virtual precision, and rounding the perturbed result
 back to the original precision.  
We simulated within-tool software variability (WT) by running the same analyses three
times using Fuzzy Libmath with a virtual precision of $t=53$~bits for
double-precision values and $t=24$~bits for single-precision values. 
These values were chosen such that the numerical perturbation simulates machine error.
%an upper bound on the relative error between a real number and its floating-point representation.
% \camille{Given the target journal where any readers (like myself :) ) won't be expert in nuemrical perturbations, I think that you could add a bit more details here on why those numbers are good to simulate machine errors}.
The resulting samples are equally plausible estimates of
the true numerical result at the precision used by the pipelines. 
% \yohan{How can you assert that when you don't have ground truth? Would it be more safe to say "plausible estimates numerical solutions"?}
% \tristan{This does not refer to the ground truth but to the true \emph{numerical} result}
% Moreover, to evaluate numerical perturbations at different magnitudes,
% we repeated the FSL analyses for virtual
% precisions ranging from $t=1$~bit to $t=24$~bits for single-precision
% and double-precision values. We also repeated the FSL analyses for virtual
% precisions ranging from $t=24$~bits to $t=53$~bits for double-precision values, having
% set the virtual precision to $t=24$~bits for single-precision values.

>>>>

\begin{equation}
  N = (-1)^s \times 2^E \times (1.m),
\end{equation}
where $E=e-127$ for single precision and $E=e-1023$ for double precision.
In single precision, the pseudo-mantissa has 23 bits and the exponent has 8 bits, whereas in 
double precision the pseudo-mantissa has 52 bits and the exponent has 11 bits. 
Machine error, the smallest absolute difference between two
floating-point numbers that can be represented, is in general $2^{-24}\times e$ in
single precision and $2^{-53}\times e$ in double precision.
We simulated machine error by introducing the random perturbation defined
in Equation~\ref{eq:mca_inexact} at the virtual precision of $t=24$~bits for single-precision 
values and $t=53$~bits for double-precision ones. The perturbed pseudo-mantissa
is obtained by extending the size of the original pseudo-mantissa, applying the perturbation 
at the desired virtual precision, and rounding the perturbed result
 back to the original precision.  
We simulated within-tool software variability (WT) by running the same analyses three
times using Fuzzy Libmath with a virtual precision of $t=53$~bits for
double-precision values and $t=24$~bits for single-precision values. 
These values were chosen such that the numerical perturbation simulates machine error.
%an upper bound on the relative error between a real number and its floating-point representation.
% \camille{Given the target journal where any readers (like myself :) ) won't be expert in nuemrical perturbations, I think that you could add a bit more details here on why those numbers are good to simulate machine errors}.
The resulting samples are equally plausible estimates of
the true numerical result at the precision used by the pipelines. 
% \yohan{How can you assert that when you don't have ground truth? Would it be more safe to say "plausible estimates numerical solutions"?}
% \tristan{This does not refer to the ground truth but to the true \emph{numerical} result}
% Moreover, to evaluate numerical perturbations at different magnitudes,
% we repeated the FSL analyses for virtual
% precisions ranging from $t=1$~bit to $t=24$~bits for single-precision
% and double-precision values. We also repeated the FSL analyses for virtual
% precisions ranging from $t=24$~bits to $t=53$~bits for double-precision values, having
% set the virtual precision to $t=24$~bits for single-precision values.
